Verifying Demonstrations

### 2017-10-04 protocol.tex
Moves discussion of NIZK proof to submission time
Improves proof overview figure (fixes #41)

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=left,level distance=5em}
    \Tree [.proof
    {share}
    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
    %[.tsig {$t_s''$} ]
    ]
    {share}
    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.
She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
computations below) whereas the \ac{NIZK} proof will be used separately to prove 
the validity (eligibility) of \(pid\).

@@

>>>>

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}[<-,item/.style={rectangle,draw}]
    \tikzset{%
      %grow'=left,%
      %level distance=5em%
    }
    \node[item] (proof) {Proof share}
      child {%
        node[item] (pid) {$pid$}
        child {%
          node[item] (cid) {$cid$}
          child {%
            node[item] (manifesto) {Manifesto}
          }
        }
      }
      child {%
        node[item] (ts) {$t_s$}
      }
      child {%
        node[item] (l) {$l$}
      }
      child {%
        node[item] (wid) {$wid$}
      }
      ;

      \path[every node/.style={font=\small}]
      (wid) edge[bend left] node [anchor=north] {$PRF_{k_w}(\cdot)$} (pid)
      (cid) edge node [anchor=east] {$H(\cdot)$} (manifesto)
      (pid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (cid)
      ;

%    \Tree [.proof
%    {share}
%    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
%    %[.tsig {$t_s''$} ]
%    ]
%    {share}
%    ]
  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    The proof depends on several proof shares.
    Each share depends on the protester's identifier (\(pid\), which depends on 
    the cause identifier, \(cid\)),
    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
    identifier (\(wid\)).
  }}%
  \label{fig:ProofFig}
\end{figure}
\end{frame}

@@

Next we need to consider the protesters' identifiers to prevent Sybil attacks.
\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
which allows anonymous authentication at most \(n\) times\footnote{%
  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
  \Textcite{Psignatures}, see issue \#27.
}.
Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
national identity-card (by assumption).
She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
identity during the protest.

@@

Alice must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
knows a signature by the identity authority on \(k\).
Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
computations below) whereas the \ac{NIZK} proof will be used separately to prove 
the validity (eligibility) of \(pid\).
